---
title: "COVID_19_PREPROCESSING DATA"
author: "Lasse Hansen"
date: "4/30/2021"
output: html_document
---

```{r Loading Packages}
#Install the required packages from github:
#install.packages("devtools")

#devtools::install_github("klmr/modules", force = T) # for  loading the functions i made for loading DMI data including their documentation

#install.packages("pacman")
pacman::p_load(tidyverse, 
               purrr, 
               tidyr, 
               stringr, 
               Boruta, 
               ggplot2,
               sandwich,
               survival,
               car,
               ggpubr,
               pracma,
               effects
               )
CM <- modules::import("COVID_MODEL_helpfuns", attach = T, doc = T) #Loading my own DMI module
modules::reload(CM) # this simply reloads the module in case of any changes

```

### Loading DMI Weather Variables

## YOU NEED DATA FROM https://dmigw.govcloud.dk/metObs/v1/bulk/?api-key=e32551a3-e242-45ae-8480-6129201f9a4c TO RUN THIS STEP

```{r Using function}
data <- list.files(path = "/Users/lassehansen/Desktop/Lasse/Cognitive Science 3 Semester/Causal Inference/Causal-Inference/DMI/", pattern = ".txt") %>%
    purrr::map_df(PreProc) #Using the module to load all DMI files (1 for each month) at a time

 #Data is saved in the file called 'DMI_DATA_CLEAN.csv'
```
```{r}
write.csv(data, "DMI_DATA_CLEAN.csv")
data <- read_csv("DMI_DATA_CLEAN.csv")
```

#### Making sure that each municipality has a date

```{r Adding municipalities without weather data}
sub <- subset(data, Kommune == "Tønder")
sub[, 2:7] <- "NA"
sub$Kommune <- "Kolding"
sub$Kolonne1 <- "10"

sub1 <- sub
sub1$Kommune <- "Ærø"
sub1$Kolonne1 <- "14"

sub2 <- sub1
sub2$Kommune <- "Albertslund"
sub2$Kolonne1 <- "19"

sub3 <- sub1
sub3$Kommune <- "Allerød"
sub3$Kolonne1 <- "19"

sub4 <- sub1
sub4$Kommune <- "Ballerup"
sub4$Kolonne1 <- "19"

sub5 <- sub1
sub5$Kommune <- "Brøndby"
sub5$Kolonne1 <- "19"

sub41 <- sub1
sub41$Kommune <- "Brønderslev"
sub41$Kolonne1 <- "1"

sub42 <- sub1
sub42$Kommune <- "Christiansø"
sub42$Kolonne1 <- "14"

sub44 <- sub1
sub44$Kommune <- "DMI"
sub44$Kolonne1 <- "19"


sub6 <- sub1
sub6$Kommune <- "Dragør"
sub6$Kolonne1 <- "19"

sub7 <- sub1
sub7$Kommune <- "Egedal"
sub7$Kolonne1 <- "19"

sub8 <- sub1
sub8$Kommune <- "Frederiksberg"
sub8$Kolonne1 <- "19"

sub9 <- sub1
sub9$Kommune <- "Frederikssund"
sub9$Kolonne1 <- "18"

sub10 <- sub1
sub10$Kommune <- "Gladsaxe"
sub10$Kolonne1 <- "19"

sub11 <- sub1
sub11$Kommune <- "Glostrup"
sub11$Kolonne1 <- "19"

sub12 <- sub1
sub12$Kommune <- "Halsnæs"
sub12$Kolonne1 <- "18"


sub13 <- sub1
sub13$Kommune <- "Herlev"
sub13$Kolonne1 <- "19"


sub14 <- sub1
sub14$Kommune <- "Helsingør"
sub14$Kolonne1 <- "19"


sub15 <- sub1
sub15$Kommune <- "Hørsholm"
sub15$Kolonne1 <- "19"


sub16 <- sub1
sub16$Kommune <- "Hvidovre"
sub16$Kolonne1 <- "19"


sub17 <- sub1
sub17$Kommune <- "Ishøj"
sub17$Kolonne1 <- "19"


sub18 <- sub1
sub18$Kommune <- "Jammerbugt"
sub18$Kolonne1 <- "2"

sub19 <- sub1
sub19$Kommune <- "Lejre"
sub19$Kolonne1 <- "18"


sub20 <- sub1
sub20$Kommune <- "Lemvig"
sub20$Kolonne1 <- "4"

sub21 <- sub1
sub21$Kommune <- "Lyngby-Taarbæk"
sub21$Kolonne1 <- "19"

sub22 <- sub1
sub22$Kommune <- "Rebild"
sub22$Kolonne1 <- "2"

sub23 <- sub1
sub23$Kommune <- "Rødovre"
sub23$Kolonne1 <- "19"

sub24 <- sub1
sub24$Kommune <- "Roskilde"
sub24$Kolonne1 <- "17"

sub25 <- sub1
sub25$Kommune <- "Rudersdal"
sub25$Kolonne1 <- "19"

sub26 <- sub1
sub26$Kommune <- "Solrød"
sub26$Kolonne1 <- "17"

sub27 <- sub1
sub27$Kommune <- "Sorø"
sub27$Kolonne1 <- "16"

sub28 <- sub1
sub28$Kommune <- "Stevns"
sub28$Kolonne1 <- "17"

sub29 <- sub1
sub29$Kommune <- "Vallensbæk"
sub29$Kolonne1 <- "19"

sub100 <- sub1
sub100$Kommune <- "Vejle"
sub100$Kolonne1 <- "11"

sub101 <- sub1
sub101$Kommune <- "Billund"
sub101$Kolonne1 <- "7"

sub45 <- sub1
sub45$Kommune <- "Greve"
sub45$Kolonne1 <- "17"

sub46 <- sub1
sub46$Kommune <- "Fredensborg"
sub46$Kolonne1 <- "19"

sub47 <- sub1
sub47$Kommune <- "Hillerød"
sub47$Kolonne1 <- "19"

sub48 <- sub1
sub48$Kommune <- "Høje-Taastrup"
sub48$Kolonne1 <- "19"

sub49 <- sub1
sub49$Kommune <- "Odense"
sub49$Kolonne1 <- "12"

sub50 <- sub1
sub50$Kommune <- "Langeland"
sub50$Kolonne1 <- "14"

sub51 <- sub1
sub51$Kommune <- "Faxe"
sub51$Kolonne1 <- "17"

sub52 <- sub1
sub52$Kommune <- "Ringsted"
sub52$Kolonne1 <- "18"

sub53 <- sub1
sub53$Kommune <- "Kerteminde"
sub53$Kolonne1 <- "12"

sub54 <- sub1
sub54$Kommune <- "Morsø"
sub54$Kolonne1 <- "12"

sub55 <- sub1
sub55$Kommune <- "Odder"
sub55$Kolonne1 <- "11"

sub56 <- sub1
sub56$Kommune <- "Vejen"
sub56$Kolonne1 <- "9"

sub57 <- sub1
sub57$Kommune <- "Mariagerfjord"
sub57$Kolonne1 <- "2"

sub58 <- sub1
sub58$Kommune <- "Struer"
sub58$Kolonne1 <- "4"

sub59 <- sub1
sub59$Kommune <- "Fredensborg"
sub59$Kolonne1 <- "19"

sub60 <- sub1
sub60$Kommune <- "Gribskov"
sub60$Kolonne1 <- "19"



bind <- rbind(sub, sub1, sub2, sub3, sub4, sub5, sub6, sub7, sub8, sub9, sub10, sub11, sub12, sub13, sub14, sub15, sub16, sub17, sub18, sub19, sub20, sub21, sub22, sub23, sub24, sub25, sub26, sub27, sub28, sub29, sub40, sub41, sub42, sub44, sub45, sub46, sub47, sub48, sub49, sub50, sub51, sub52, sub53, sub54, sub55, sub56, sub57, sub58, sub100, sub101, sub59, sub60)

bind$stationID <- as.numeric(bind$stationID)
bind$humidity_past1h <-  as.numeric(bind$humidity_past1h)
bind$precip_dur_past1h <-  as.numeric(bind$precip_dur_past1h)
bind$sun_last1h_glob <-  as.numeric(bind$sun_last1h_glob)
bind$temp_mean_past1h <-  as.numeric(bind$temp_mean_past1h)
bind$wind_speed_past1h <-  as.numeric(bind$wind_speed_past1h)

data111 <- left_join(data, kommune)
data111$Kommune_Nummer <- NULL
bind$Date <- as.Date(bind$Date)
bind$Kolonne1 <- as.integer(bind$Kolonne1)
data111$Date <- as.Date(data111$Date)
data10 <- rbind(bind, data111)
data10$Kommune = ifelse(data10$Kommune == "6052", "Lemvig", data10$Kommune)
data9 <- data10 %>% select(Date, Kommune)

write.csv(data10, "data.10.csv")
write.csv(data9, "data9.csv")
```

### Reading Google Mobility Data - Cleaning it to match Municipality names

```{r Loading 2020 mobility data from google}
mobility <- read_csv("2020_DK_Region_Mobility_Report1.csv")

mobility$CountDate <- as.numeric(mobility$date)

mobility$sub_region_2 <- gsub(" Municipality", "", mobility$sub_region_2)
mobility$sub_region_2 <- gsub(" ", "", mobility$sub_region_2)

mobility_region = mobility %>% filter(is.na(.$sub_region_2)) %>% filter(!is.na(.$sub_region_1)) %>% select(sub_region_1, date, 10:16)

mobility$sub_region_2 <- ifelse(mobility$sub_region_2 == "Vesthimmerland", "Vesthimmerlands", mobility$sub_region_2)

mobility$sub_region_2 <- ifelse(mobility$sub_region_2 == "Brondby", "Brøndby", mobility$sub_region_2)

mobility$sub_region_2 <- ifelse(mobility$sub_region_2 == "Copenhagen", "København", mobility$sub_region_2)

mobility$sub_region_2 <- ifelse(mobility$sub_region_2 == "Nordfyn", "Nordfyns", mobility$sub_region_2)

mobility = mobility %>% filter(!is.na(sub_region_2))

mobility <- mobility %>% select(date, sub_region_1, sub_region_2, residential_percent_change_from_baseline, workplaces_percent_change_from_baseline, transit_stations_percent_change_from_baseline, retail_and_recreation_percent_change_from_baseline, parks_percent_change_from_baseline, grocery_and_pharmacy_percent_change_from_baseline)

colnames(mobility) <- c("Date", "Region", "Kommune", "Residential", "Workplace", "Transit", "Retail", "Park", "Grocery")
```

```{r Loading 2021 mobility data from google}
mobility1 <- read_csv("2021_DK_Region_Mobility_Report.csv")

mobility1$CountDate <- as.numeric(mobility1$date)

mobility1$sub_region_2 <- gsub(" Municipality", "", mobility1$sub_region_2)
mobility1$sub_region_2 <- gsub(" ", "", mobility1$sub_region_2)

mobility_region2020 = mobility1 %>% filter(is.na(.$sub_region_2)) %>% filter(!is.na(.$sub_region_1)) %>% select(sub_region_1, date, 10:16)

mobility1$sub_region_2 <- ifelse(mobility1$sub_region_2 == "Vesthimmerland", "Vesthimmerlands", mobility1$sub_region_2)

mobility1$sub_region_2 <- ifelse(mobility1$sub_region_2 == "Brondby", "Brøndby", mobility1$sub_region_2)

mobility1$sub_region_2 <- ifelse(mobility1$sub_region_2 == "Copenhagen", "København", mobility1$sub_region_2)

mobility1$sub_region_2 <- ifelse(mobility1$sub_region_2 == "Nordfyn", "Nordfyns", mobility1$sub_region_2)

mobility1 = mobility1 %>% filter(!is.na(sub_region_2))


mobility1 <- mobility1 %>% select(date, sub_region_1, sub_region_2, residential_percent_change_from_baseline, workplaces_percent_change_from_baseline, transit_stations_percent_change_from_baseline, retail_and_recreation_percent_change_from_baseline, parks_percent_change_from_baseline, grocery_and_pharmacy_percent_change_from_baseline)

colnames(mobility1) <- c("Date", "Region", "Kommune", "Residential", "Workplace", "Transit", "Retail", "Park", "Grocery")

mobility2 <- rbind(mobility, mobility1)
mobility20 <- rbind(mobility_region, mobility_region2020)
mobility11 <- left_join(data9, mobility2, by = c("Kommune", "Date"))
mobility20 = mobility20 %>% rename(Date = date)
mobility20 = mobility20 %>% rename(Region = sub_region_1)
```

### Using Region Identifier function to replace data if necessary

```{r}
mobility11 <- CM$Region_identifier(mobility11)
```

### If municipality does not contain data for a date, replace with region mean for the day

```{r Making sure every region has every date}

join = left_join(mobility11, mobility20, by = c("Region", "Date"))

join$Residential = ifelse(is.na(join$Residential), join$residential_percent_change_from_baseline, join$Residential)

join$Transit = ifelse(is.na(join$Transit), join$transit_stations_percent_change_from_baseline, join$Transit)

join$Retail = ifelse(is.na(join$Retail), join$retail_and_recreation_percent_change_from_baseline, join$Retail)

join$Workplace = ifelse(is.na(join$Workplace), join$workplaces_percent_change_from_baseline, join$Workplace)

mobility_dat = join %>% subset(.$Kommune != "Christiansø")
mobility_dat = mobility_dat %>% subset(.$Kommune != "DMI")
mobility_dat = mobility_dat %>% select(Date, Kommune, Region, Transit, Residential, Retail, Workplace)

mobility_dat = mobility_dat %>% group_by(Date, Kommune) %>% 
  summarise(
    Transit = mean(Transit),
    Residential = mean(Residential),
    Retail = mean(Retail),
    Workplace = mean(Workplace)
  )
  
  
write_csv(mobility_dat, "mobility_dat.csv") #Data is saved as 'mobility_dat.csv' for your use
```

### Merging mobility data and weather data for each municipality

```{r Taking mean of weather variables per weather station in municipalities}
kommune  <- read.csv("Kommuneposition (1).csv", sep = ";") 

data1 <- full_join(data10, kommune, by = "Kommune", "Date")

data1$Kolonne1 <- ifelse(is.na(data1$Kolonne1.x), data1$Kolonne1.y, data1$Kolonne1.x)
data1$Kolonne1.y <- NULL
data1$Kolonne1.x <- NULL

data1 <- filter(data1, Kommune != "DMI") # Filtering out two datapoints that we do not need for analysis
data1 <- filter(data1, Kommune != "Christiansø")
data4 <- data1 %>% 
  select(Date, Kommune, humidity_past1h, precip_dur_past1h, sun_last1h_glob, temp_mean_past1h, Kolonne1, wind_speed_past1h) %>% 
  group_by(Kolonne1, Date) %>% 
  summarise(
    Humid = mean(humidity_past1h, na.rm = T),
    Precip = mean(precip_dur_past1h, na.rm = T),
    Sun = mean(sun_last1h_glob, na.rm = T),
    Temp = mean(temp_mean_past1h, na.rm = T),
    Wind = mean(wind_speed_past1h, na.rm = T),
    Kommune = Kommune
            )

data4 <- data4 %>% 
  group_by(Date, Kommune) %>% 
  summarise(
    Humid = mean(Humid, na.rm = T),
    Precip = mean(Precip, na.rm = T),
    Sun = mean(Sun, na.rm = T),
    Temp = mean(Temp, na.rm = T),
    Wind = mean(Wind, na.rm = T),
            )


data4 <- left_join(mobility_dat, data4, by = c("Kommune" = "Kommune", "Date" = "Date"))

data4 <- filter(data4, Kommune != "DMI")
```


### Loading Municipality time series of cases from SSI

```{r}

positive <- read.csv("Municipality_cases_time_series.csv", sep = ";")
positive$NA. <- NULL

positive <- positive[complete.cases(positive), ]
positive <- positive %>% pivot_longer(., 2:99)
colnames(positive) <- c("Date", "Kommune", "Cases")

positive$Kommune <- ifelse(positive$Kommune == "Copenhagen", "København",
                  ifelse(positive$Kommune == "Høje.Taastrup", "Høje-Taastrup",
                  ifelse(positive$Kommune == "Lyngby.Taarbæk", "Lyngby-Taarbæk",
                  ifelse(positive$Kommune == "Faaborg.Midtfyn", "Faaborg-Midtfyn",
                  ifelse(positive$Kommune == "Ikast.Brande", "Ikast-Brande",
                  ifelse(positive$Kommune == "Ringkøbing.Skjern", "Ringkøbing-Skjern",
                  ifelse(positive$Kommune == "Copenhagen", "København", positive$Kommune
                         )))))))

positive <- filter(positive, Kommune != "DMI")


positive$Date <- as.factor(positive$Date)

data5 <- left_join(data4, positive)
```

### Loading Oxford Stringency Index

```{r Reading in stringency index}
string <- read_csv("covid-stringency-index (1).csv")
string = string %>% filter(., Entity == "Denmark")
string$Date <- as.Date(string$Day)
string$Entity <- NULL
string$Code <- NULL
```

### Moving onto loading data from DKSTAT

```{r Getting devtools for dkstat}
if(!require("devtools")) install.packages("devtools")

library("devtools")

install_github("rOpenGov/dkstat", force =TRUE )

library(dkstat)

table<- dst_get_tables(lang = "da")
aulaar_meta <- dst_meta(table = "AREALDK", lang = "da")
```

#### Loading builded areas variable

```{r}
Befolk <- dst_get_data(table = "AREALDK", ARE1 = "Bygninger og bebyggede områder" , ENHED = "Kvadratmeter (m2) pr. indbygger",  OMRÅDE = "*", Tid = "2018")
Befolk$Kommune = Befolk$OMRÅDE
Befolk$Bebyggelse = Befolk$value
Befolk = Befolk %>% select(Kommune, Bebyggelse)
```

#### Loading Number of Young Adults

```{r Getting age characteristics}
city <- dst_get_data(table = "BY2" , KOMK = "*", ALDER = "*", KØN = "*", Tid = "2020")
city$ALDER <- gsub("år", "", city$ALDER)

colnames(city) <- c("Kommune", "Alder", "Køn", "Date", "Antal_Gruppe")

city$Alder <- as.numeric(city$Alder)

city <- subset(city, Alder <= 100)

city <- subset(city, Kommune != "Christiansø")

city1 <- city %>% 
     mutate(Alder = ifelse(Alder >= 19 & Alder < 30, "Under_30",
                      ifelse(Alder >= 30 & Alder < 110, "Over_30", "h"))) %>% 
     group_by(Kommune, Alder) %>% 
     summarise(
       Antal = sum(Antal_Gruppe)
     )       
                           

city <- city1 %>% group_by(Kommune, Alder) %>% 
     pivot_wider(., 1:3, names_from = Alder, values_from = Antal) 

city <- city %>% mutate(
       Total = Under_30 + Over_30 + h,
       Under_30 = (Under_30/Total)*100,
       Over_30 = (Over_30/Total)*100)
```

### Reading Municipality Population Number

```{r}
BY3 <- read_csv("BY3.csv") #Avaliable in materials
```

#### Making lagged variables for analysis 

```{r}
data7 <- data5 %>% group_by(Kommune) %>% mutate(
  Humid_lag = lag(Humid, 9),
  Temp_lag = lag(Temp, 9),
  Precip_lag = lag(Precip, 9),
  Cases_lag9 = lag(Cases, 9),
  Retail_Change_lag = lag(Retail, 9),
  Transit_Change_lag = lag(Transit, 9), 
  Residential_Change_lag = lag(Residential, 9),
  Workplace_Change_lag = lag(Workplace, 9)
  )
```

### Joining all variables for analysis

```{r Joining it all for the analysis}

join1 <- full_join(BY3, city, by = c("Kommune"))
join2 <- left_join(join1, Befolk, by = "Kommune")
d7 <- left_join(data7, string, by = "Date")
d8 <- full_join(d7, join2, by = c("Kommune"))
d7 = d8
d8$Week <- strftime(d8$Date, format = "%Y-W%V")
d8$CountDate <- as.Date(d8$Date, format= "%Y-%m-%d")
d8 = d8 %>% subset(Kommune != "Christiansø")

```

### Making lagged variables, rolling averages, filtering dates, and scaling data

```{r}
d9 = d8 %>% ungroup() %>% mutate(
  Stringency = lag(stringency_index, 9),
  Cases = ((100000/Befolkningstal)*Cases),
  Cases_lag9 = ((100000/Befolkningstal)*Cases_lag9),
  Cases_lag9 = movavg(Cases_lag9, n = 7, type = "s"),
  Precip_lag= movavg(Precip_lag, n = 7, type = "s"),
  Temp_lag= movavg(Temp_lag, n = 7, type = "s"),
  Humid_lag= movavg(Humid_lag, n = 7, type = "s"),
  Transit_Change_lag= movavg(Transit_Change_lag, n = 7, type = "s"),
  Work_Change_lag= movavg(Workplace_Change_lag, n = 7, type = "s"),
  Retail_Change_lag= movavg(Retail_Change_lag, n = 7, type = "s"),
  Residential_Change_lag= movavg(Residential_Change_lag, n = 7, type = "s"),
  Cases = movavg(Cases, n = 7, type = "s"),
) %>% select(Cases_lag9 , Stringency, Bebyggelse, Over_30 , Transit_Change_lag , Residential_Change_lag, Kommune, Date, Week, Under_30, Cases, Temp_lag, Precip_lag, Work_Change_lag, Retail_Change_lag, Befolkningstæthed)

d9 = d9 %>%  subset(.$Date >= "2020-09-01" & .$Date <= "2021-02-28") #Subsetting the dates needed for analysis

d9$Stringency = scale(d9$Stringency)
d9$Cases_lag9 = scale(d9$Cases_lag9)
d9$Precip_lag = scale(d9$Precip_lag)
d9$Temp_lag = scale(d9$Temp_lag)
d9$Transit_Change_lag = scale(d9$Transit_Change_lag)
d9$Work_Change_lag = scale(d9$Work_Change_lag)
d9$Retail_Change_lag = scale(d9$Retail_Change_lag)
d9$Residential_Change_lag = scale(d9$Residential_Change_lag)
d9$Under_30 = scale(d9$Under_30)
d9$Befolkningstæthed = scale(d9$Befolkningstæthed)
d9$Bebyggelse = scale(d9$Bebyggelse)

d10 = d9 %>% drop_na() #dropping na's

mean(d9$Stringency) #testing that scaling works

write_csv(d10, "data_for_analysis.csv")
```
