---
title: "The effect of social mobility dynamics on Covid-19"
author: "Lasse Hyldig Hansen"
date: "4/30/2021"
output: html_document
---

### Reading in data from preprocessing script

```{r}
d10 = read_csv("data_for_analysis.csv")
```


### Running the two models (Null and Full model)

```{r}
reg1 <- lmer(data = d10, Cases ~ (Cases_lag9  +  Residential_Change_lag + Transit_Change_lag + Precip_lag + Temp_lag)*Stringency + Bebyggelse + Under_30 + (1|Date) + (1 | Kommune))
reg2 <- lm(data = d10, Cases ~ Cases_lag9 * Stringency)
```

### Getting Marginal and Conditional Rsquared

```{r}
MuMIn::r.squaredGLMM(reg1)
```

### Getting Summary Statistics

```{r}
summary(reg1)
summary(reg2)
```

### Model Comparison

```{r}
anova(reg1, reg2)
```

### Making Interaction plots

```{r}
Inter.HandPick1 <- effect('Temp_lag:Stringency', reg1, 
                                              xlevels=list(Temp_lag = c(-1, 0, 1),
                                              Stringency = c(-1, 0, 1)),
                                              se=TRUE, confidence.level=.95, typical=mean)

Inter.HandPick1 = data.frame(Inter.HandPick1)

Inter.HandPick1$Stringency = ifelse(Inter.HandPick1$Stringency == -1, "Low Stringency", 
                            ifelse(Inter.HandPick1$Stringency == 0, "Mean Stringency", "High Stringency"))

Inter.HandPick1$Temp_lag = ifelse(Inter.HandPick1$Temp_lag == -1, "Low Temperature", 
                            ifelse(Inter.HandPick1$Temp_lag == 0, "Mean Temperature", "High Temperature"))

Inter.HandPick1$Temp_lag <- factor(Inter.HandPick1$Temp_lag, levels = c("Low Temperature", "Mean Temperature", "High Temperature"))
Inter.HandPick1$Stringency <- factor(Inter.HandPick1$Stringency, levels = c("Low Stringency", "Mean Stringency", "High Stringency"))
geom.text.size = 8
theme.size = (14/5) * geom.text.size

p1<- ggplot(Inter.HandPick1, aes(x=Temp_lag, y=fit, group=Stringency, color=Stringency)) + 
  geom_line() +
  geom_point()+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=.1,
                 ) + scale_color_manual(values=c('#ffd882','#c4c4c4', '#15607a')) +
  labs("Interaction effect of Stringency and Temperature", x="", y = "Cases per 100,000 capita") + theme(axis.text = element_text(size = theme.size)) + theme_light()
```

```{r Plot Cases interaction}
Inter.HandPick2 <- effect('Cases_lag9:Stringency', reg1, 
                                              xlevels=list(Cases_lag9 = c(-1, 0, 1),
                                              Stringency = c(-1, 0, 1)),
                                              se=TRUE, confidence.level=.95, typical=mean)
Inter.HandPick2 = data.frame(Inter.HandPick2)

Inter.HandPick2$Stringency = ifelse(Inter.HandPick2$Stringency == -1, "Low Stringency", 
                            ifelse(Inter.HandPick2$Stringency == 0, "Mean Stringency", "High Stringency"))

Inter.HandPick2$Cases_lag9 = ifelse(Inter.HandPick2$Cases_lag9 == -1, "Low number of Cases", 
                            ifelse(Inter.HandPick2$Cases_lag9 == 0, "Mean number of Cases", "High number of Cases"))

Inter.HandPick2$Cases_lag9 <- factor(Inter.HandPick2$Cases_lag9, levels = c("Low number of Cases", "Mean number of Cases", "High number of Cases"))
Inter.HandPick2$Stringency <- factor(Inter.HandPick2$Stringency, levels = c("Low Stringency", "Mean Stringency", "High Stringency"))


p2<- ggplot(Inter.HandPick2, aes(x=Cases_lag9, y=fit, group=Stringency, color=Stringency)) + 
  geom_line() +
  geom_point()+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=.1,
                 ) + scale_color_manual(values=c('#ffd882','#c4c4c4', '#15607a')) +
  labs("Interaction effect of Stringency and autoregresive Cases", x="", y = "Cases per 100,000 capita") + theme(axis.text = element_text(size = theme.size))+ theme_light()
```


```{r}
Inter.HandPick3 <- effect('Precip_lag:Stringency', reg1, 
                                              xlevels=list(Precip_lag = c(-1, 0, 1),
                                              Stringency = c(-1, 0, 1)),
                                              se=TRUE, confidence.level=.95, typical=mean)
Inter.HandPick3 = data.frame(Inter.HandPick3)

Inter.HandPick3$Stringency = ifelse(Inter.HandPick3$Stringency == -1, "Low Stringency", 
                            ifelse(Inter.HandPick3$Stringency == 0, "Mean Stringency", "High Stringency"))

Inter.HandPick3$Precip_lag = ifelse(Inter.HandPick3$Precip_lag == -1, "Low Precipitation", 
                            ifelse(Inter.HandPick3$Precip_lag == 0, "Mean Precipitation", "High Precipitation"))

Inter.HandPick3$Precip_lag <- factor(Inter.HandPick3$Precip_lag, levels = c("Low Precipitation", "Mean Precipitation", "High Precipitation"))
Inter.HandPick3$Stringency <- factor(Inter.HandPick3$Stringency, levels = c("Low Stringency", "Mean Stringency", "High Stringency"))


p3<- ggplot(Inter.HandPick3, aes(x=Precip_lag, y=fit, group=Stringency, color=Stringency)) + 
  geom_line() +
  geom_point()+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=.1,
                 ) + scale_color_manual(values=c('#ffd882','#c4c4c4', '#15607a')) +
  labs("Interaction effect of Stringency and Precipitation", x="", y = "Cases per 100,000 capita") + theme(axis.text = element_text(size = theme.size))+ theme_light()
```

```{r}

Inter.HandPick4 <- effect('Residential_Change_lag:Stringency', reg1, 
                                              xlevels=list(Residential_Change_lag = c(-1, 0, 1),
                                              Stringency = c(-1, 0, 1)),
                                              se=TRUE, confidence.level=.95, typical=mean)
Inter.HandPick4 = data.frame(Inter.HandPick4)

Inter.HandPick4$Stringency = ifelse(Inter.HandPick4$Stringency == -1, "Low Stringency", 
                            ifelse(Inter.HandPick4$Stringency == 0, "Mean Stringency", "High Stringency"))

Inter.HandPick4$Residential_Change_lag = ifelse(Inter.HandPick4$Residential_Change_lag == -1, "Low Residential Mobility", 
                            ifelse(Inter.HandPick4$Residential_Change_lag == 0, "Mean Residential Mobility", "High Residential Mobility"))

Inter.HandPick4$Residential_Change_lag <- factor(Inter.HandPick4$Residential_Change_lag, levels = c("Low Residential Mobility", "Mean Residential Mobility", "High Residential Mobility"))
Inter.HandPick4$Stringency <- factor(Inter.HandPick4$Stringency, levels = c("Low Stringency", "Mean Stringency", "High Stringency"))


p4<- ggplot(Inter.HandPick4, aes(x=Residential_Change_lag, y=fit, group=Stringency, color=Stringency)) + 
  geom_line() +
  geom_point()+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=.1,
                 ) + scale_color_manual(values=c('#ffd882','#c4c4c4', '#15607a')) +
  labs("Interaction effect of Stringency and Residential Mobility Change", x="", y = "Cases per 100,000 capita")+ theme(axis.text = element_text(size = theme.size))+theme_light()
```

```{r}
Inter.HandPick5 <- effect('Transit_Change_lag:Stringency', reg1, 
                                              xlevels=list(Transit_Change_lag = c(-1, 0, 1),
                                              Stringency = c(-1, 0, 1)),
                                              se=TRUE, confidence.level=.95, typical=mean)
Inter.HandPick5 = data.frame(Inter.HandPick5)

Inter.HandPick5$Stringency = ifelse(Inter.HandPick5$Stringency == -1, "Low Stringency", 
                            ifelse(Inter.HandPick5$Stringency == 0, "Mean Stringency", "High Stringency"))

Inter.HandPick5$Transit_Change_lag = ifelse(Inter.HandPick5$Transit_Change_lag == -1, "Low Transit Mobility", 
                            ifelse(Inter.HandPick5$Transit_Change_lag == 0, "Mean Transit Mobility", "High Transit Mobility"))

Inter.HandPick5$Transit_Change_lag <- factor(Inter.HandPick5$Transit_Change_lag, levels = c("Low Transit Mobility", "Mean Transit Mobility", "High Transit Mobility"))
Inter.HandPick5$Stringency <- factor(Inter.HandPick5$Stringency, levels = c("Low Stringency", "Mean Stringency", "High Stringency"))


p5<- ggplot(Inter.HandPick5, aes(x=Transit_Change_lag, y=fit, group=Stringency, color=Stringency)) + 
  geom_line() +
  geom_point()+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=.1,
                 ) + scale_color_manual(values=c('#ffd882','#c4c4c4', '#15607a')) +
  labs("Interaction effect of Stringency and Transit Mobility Change", x="", y = "Cases per 100,000 capita") + theme(axis.text = element_text(size = theme.size))+ theme_light()
```

### Two figures from Paper

```{r}
figure1 = ggarrange(p1, p4,labels = c("a","b"), ncol = 2, nrow = 1, common.legend = T) + theme(axis.text = element_text(size = theme.size))+ theme_light()
figure1
```


```{r}
figure2 = ggarrange(p2,p3, p5, labels = c("a","b", "c"), ncol = 2, nrow = 2, common.legend = T) + theme(axis.text = element_text(size = theme.size))+ theme_light()
figure2
```


### Getting predicted values from the two models

```{r}
d10$Full_Model <- fitted(reg1, d10)
d10$Null_Model <- fitted(reg2, d10)
```

### Making dataframe for visualizing some random municipalities for visuals from paper

```{r}
d11 = d10 %>% filter(.$Kommune %in% c("Sønderborg", "Varde", "Brøndby", "København"))
```

### Plotting fitted values from both models compared to actual cases for the four aforementioned municipalities 

```{r}
fitted_plot = ggplot(data = d11, aes(Date, )) +
  geom_smooth(aes(y = Cases, colour = "Cases",level = 0.95)) +
  geom_smooth(aes(y = Full_Model, colour = "Full_Model", level = 0.95)) +
  geom_smooth(aes(y = Null_Model, colour = "Null_Model", level = 0.95)) +
  facet_wrap(~ Kommune) +
  theme(axis.text = element_text(size = theme.size))+ theme_light()
fitted_plot
```

### Plotting fitted values from both models compared to actual cases for all municipalities

```{r}
fitted_plot_all = ggplot(data = d10, aes(Date, )) +
  geom_smooth(aes(y = Cases, colour = "Cases",level = 0.95)) +
  geom_smooth(aes(y = Full_Model, colour = "Full_Model", level = 0.95)) +
  geom_smooth(aes(y = Null_Model, colour = "Null_Model", level = 0.95)) +
  facet_wrap(~ Kommune) +
  theme(axis.text = element_text(size = theme.size))+ theme_light()
fitted_plot_all
```
